Output Summary

### 2021-12-17 03-post-process/output-plots.Rmd
Add a plot showing proportion of fall migrants

>>>>

# Migratory Strategy Apportionment

```{r pi-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
```
